---
title: "linear_models"
author: "Congyu Yang"
date: "2024-11-07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type) %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )
```

## Fit some models

```{r}
fit <- lm(price ~ stars, data = nyc_airbnb)

summary(fit)

names(fit)

coef(fit)

fit %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value)

fit %>% 
  broom::glance()
```

Try a bit more complex
```{r}
fit <- 
  lm(price ~ stars + borough, data = nyc_airbnb)

summary(fit)

fit %>% 
  broom::tidy() %>% 
  select(term,estimate,p.value) %>% 
  mutate(term = str_replace(term,"borough","Borough: ")) %>% 
  knitr::kable(digits = 3)
```

## Some diagnostics

Most diagnostics use residuals

```{r}
modelr::add_residuals(nyc_airbnb,fit) %>% 
  ggplot(aes(x = borough,y = resid))+
  geom_violin()+
  ylim(-100,100)
```
Residuals against stars

```{r}
modelr::add_residuals(nyc_airbnb,fit) %>% 
  ggplot(aes(x = stars,y = resid))+
  geom_point()
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price))+
  geom_point()+
  stat_smooth(method = "lm")
```
Residuals against fitted values

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred,y = resid)) +
  geom_point()

```
## Hypothesis Testing

### anova() only helps for nested data.

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

fit_null %>% 
  broom::tidy()

fit_alt %>% 
  broom::tidy()

anova(fit_null,fit_alt) %>% 
  broom::tidy()
```
## Do effects differ across boroughs

```{r}
nyc_airbnb %>% 
  lm(price ~ stars * borough + room_type * borough,data = .) %>% 
  broom:: tidy()

lm(price ~ stars * borough + room_type * borough,data = nyc_airbnb) %>% 
  broom::tidy()
```
Could just fit separate models

```{r}
nyc_airbnb %>% filter(borough == "Brooklyn") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
  
```

```{r}
nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(model = map(data, \(x) lm(price ~ stars + room_type, data = x)),
         results = map(model,broom::tidy)) %>% 
  select(borough, results) %>% 
  unnest(results) %>% 
  select(borough,term,estimate) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  )
```

what about room type across mahattan neighborhood?

```{r}
nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    neighborhood == "Chinatown") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()

nyc_airbnb %>% 
  filter(
    borough == "Manhattan",
    neighborhood == "Chelsea") %>% 
  lm(price ~ stars + room_type, data = .) %>% 
  broom::tidy()
```

Do it for all neighborhoods!

```{r}
manhattan_nest_fit_res <- nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  nest(data = -(borough:neighborhood)) %>% 
  mutate(model = map(data,\(x) lm(price ~ stars + room_type, data = x)),
         results = map(model,broom::tidy)) %>% 
  select(neighborhood,results) %>% 
  unnest(results)
```
Look at the effect of room type
```{r}
manhattan_nest_fit_res |> 
  filter(str_detect(term, "room_type")) |> 
  ggplot(aes(x = term, y = estimate)) + 
  geom_boxplot()
```


